The paper on \Large \bf Blockchain Frontrunning

### 2018-09-04 frontrunning/Latex/setup/table.tex
[frontrunning] Top 25 Dapps Latex Table

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}

%TODO: fix the table !

\begin{table}[]
\begin{tabular}{@{}cl@{}}
\toprule
\textbf{DApp Category}                                                                               & \multicolumn{1}{c}{\textbf{DApp Names (Rank)}}                                                                                                                                                                                                                          \\ \midrule
\multicolumn{1}{|c|}{Exchanges}                                                                      & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}- IDEX (1)\\ - \textbf{ForkDelta, EtherDelta (2)}\\ - \textbf{Bancor (7)}\\ - The Token Store(13)\\ - LocalEthereum(14)\\ - Kyber (22)\end{tabular}}                                                                                       \\ \midrule
\multicolumn{1}{|c|}{\begin{tabular}[c]{@{}c@{}}Games, CryptoCollectibles \\ (ERC 721)\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}- \textbf{CryptoKitties (3)}\\ - Ethermon(4)\\ - Cryptogirl (9) \\ - Gods Unchained TCG (12) \\ - Blockchain Cuties(15) \\ - ETH.TOWN! (16) \\ - 0xUniverse (18) \\ - MLBCrypto Baseball (19) \\ - HyperDragons(25)\end{tabular}} \\ \midrule
\multicolumn{1}{|c|}{Gambling}                                                                       & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}- Fomo3D (5)\\ - DailyDivs (6)\\ - FomoWar (10)\\ - FairDapp (11)\\ - Zethr(17)\\ - dice2.win (20)\end{tabular}}                                                                                                         \\ \midrule
\multicolumn{1}{|c|}{High-Risk (Ponzi Schemes and Lotteries)}                                        & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}- PoWH 3D (8)\\ - Ether Shrimp Farm(21)\end{tabular}}                                                                                                                                                                    \\ \midrule
Misc                                                                                                 & \begin{tabular}[c]{@{}l@{}}- 0x Protocol (23)\\ - \textbf{Ethereum Name Service} (24)\end{tabular}                                                                                                                                             \\ \bottomrule
\end{tabular} 
  \caption{Top 25 DApps based on recent user activity from Dappradar.com}         \label{tab:top25dapps}                        
\end{table}

>>>>

% ------------------------------------------------------------------------------------------------------------------------------------------------%
% Top 25 Dapps Table:%

\begin{table}[t]
\centering
\begin{tabular}{|c|c|}
\hline
\textbf{DApp Category}    								& \textbf{DApp Names (Rank)} \\  \hline
\multirow{6}{*}{Exchanges} 							& IDEX (1) \\ 
												& ForkDelta, EtherDelta (2) \\
												& \textbf{Bancor (7)} \\
												& The Token Store(13) \\
												& LocalEthereum(14) \\
												& Kyber (22) \\  \hline

\multirow{9}{*}{Games, CryptoCollectibles \\ (ERC 721)}		& \textbf{CryptoKitties (3)} \\  
												& Ethermon(4)\\
												& Cryptogirl (9)\\
												& Gods Unchained TCG (12)\\
												& Blockchain Cuties(15)\\
												& ETH.TOWN! (16)\\
												& 0xUniverse (18)\\
												& MLBCrypto Baseball (19)\\
												& HyperDragons(25)\\ \hline

\multirow{6}{*}{Gambling}								& Fomo3D (5) \\  
												& DailyDivs (6) \\ 
												& FomoWar (10) \\
												& FairDapp (11)\\
												& Zethr(17) \\
												& dice2.win (20) \\
												& Kyber (22) \\  \hline
\end{tabular}
\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{Dappradar.com}.}\label{tab:top25dapps}}
\end{table}
% ------------------------------------------------------------------------------------------------------------------------------------------------%
